### 2014-04-14 docs/paper/paper.tex
initial multiplier example stuff

>>>>

As a test of a combined network with both one-dimensional and two-dimensional populations,
a neural multiplier was simulated on the hardware. Figure~\ref{lst:multiplier} shows
the code listing and the resulting network that it describes.

\begin{subfigure}[b]{\textwidth}
\centering
\lstset{language=Python}
\begin{lstlisting}[frame=single]
import nengo
import nengo.helpers
model = nengo.Model('Multiplier')
A = nengo.Ensemble(nengo.LIF(100), dimensions=1,
  radius=1.4, label='A')
B = nengo.Ensemble(nengo.LIF(100), dimensions=1,
  radius=1.4, label='B')
combined = nengo.Ensemble(nengo.LIF(224), dimensions=2,
  radius=2, label='combined')
prod = nengo.Ensemble(nengo.LIF(100), dimensions=1,
  radius=2, label='prod')

inputA = nengo.Node(nengo.helpers.piecewise
  ({0:0, 2.5:0.5, 4:-0.5}))
inputB = nengo.Node(nengo.helpers.piecewise
  ({0:1.0, 1.5:0.8, 3:0.0, 4.5:0.8}))

nengo.Connection(inputA, A)
nengo.Connection(inputB, B)

nengo.Connection(A, combined, transform=[[1],[0]])
nengo.Connection(B, combined, transform=[[0],[1]])

def product(x):
  return x[0] * x[1]

nengo.Connection(combined, prod, function=product)

A_probe = nengo.Probe(A, 'decoded_output', filter=0.01)
B_probe = nengo.Probe(B, 'decoded_output', filter=0.01)
prod_probe = nengo.Probe(prod, 'decoded_output', filter=0.01)
\end{lstlisting}
\caption{Source code}
\label{lst:multiplier:code}
\end{subfigure}

\begin{subfigure}[b]{0.3\textwidth}
\centering
% \includegraphics[width=3.0in]{multiplier-schematic.eps} % FIXME
\caption{Schematic}
\label{lst:multiplier:schematic}
\end{subfigure}

\caption[A multiplier in Nengo.]
{Source code(\ref{lst:multiplier:code}) and schematic (\ref{lst:multiplier:schematic})
of a multiplier in Nengo.}
\label{lst:multiplier}
\end{figure}

% FIXME: explain input and expected output

Simulation of this network in hardware produced results comparable to those obtained in software
(Figure~\ref{fig:multiplier}).

% FIXME software subfigure

\begin{subfigure}[b]{0.5\textwidth}
\centering
\includegraphics[width=3in]{multiplier.eps}
\caption{Hardware}
\label{fig:multiplier:hw}
\end{subfigure}

\caption[Multiplier simulation comparison.]
{Comparison of software (FIXME) and hardware (\ref{fig:multiplier:hw})
simulation of a neural multiplier network.}
\label{fig:multiplier}
\end{figure}
